Management frequency and extinction risk

### 2018-05-10 notebook/ms/SI6.Rmd
New notes

---
title: "Management frequency and extinction risk"
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Jeroen Minderman&#xb9;, Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy
  Rakotonarivo&#xb9;, Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes: null
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting
  Information 6)'
biblio-style: apalike
---

@@

For a single simulation, the `gmse_table` function prints out key information from a `gmse` simulation result. The example provided in the GMSE documentation is below.

@@

```{r, eval = FALSE}
write.csv(x= sim_table, file = "file_path/gmse_table");
```

>>>>

---
title: "Management frequency and extinction risk"
author: A. Bradley Duthie&#xb9;&#xb3;, Jeremy J. Cusack&#xb9;, Isabel L. Jones&#xb9;,
  Jeroen Minderman&#xb9;, Erlend B. Nilsen&#xb2;, Roc&#0237;o A. Pozo&#xb9;, O. Sarobidy
  Rakotonarivo&#xb9;, Bram Van Moorter&#xb2;, and Nils Bunnefeld&#xb9;
date: '[1] Biological and Environmental Sciences, University of Stirling, Stirling,
  UK [2] Norwegian Institute for Nature Research, Trondheim, Norway [3] alexander.duthie@stir.ac.uk'
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    reference_docx: docx_template.docx
header-includes:
- \usepackage{lineno}
- \linenumbers
linestretch: 1
link-citations: yes
linkcolor: blue
bibliography: gmse.bib
subtitle: 'GMSE: an R package for generalised management strategy evaluation (Supporting
  Information 6)'
biblio-style: apalike
---

@@

For a single simulation, the `gmse_table` function prints out key information from a `gmse` simulation result. The example provided in the [GMSE documentation](https://cran.r-project.org/package=GMSE) is below.

@@

```{r, eval = FALSE}
write.csv(x= sim_table, file = "file_path/gmse_table_name.csv");
```
